Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-11 paper/paper.tex
Addressing a comment in the Introduction

\Mar{@Gustavo,@Breno, can you please make this par a bit stronger
  (more coherent/compelling) as to justify the selection of these two
  techniques?}These techniques demand different effort from
developers. Cross-engine differential testing is semi-automated as
developers need to decide if alarms are manifestations of real
bugs. Test transplantation is fully automated, but it can only reveal
bugs that the original tests could reveal. This study measures the
ability of these techniques in finding bugs and the human cost
associated with each technique.

>>>>

\Mar{@Gustavo,@Breno, can you please make this par a bit stronger
  (more coherent/compelling) as to justify the selection of these two
  techniques?}
\Breno{Changed the paragraph a bit to include the reuse argument.}
We selected these two techniques because they can take advantage 
of existing test suites and reuse them --- in a semi-automated way 
as we propose here --- to enhance the coverage of the engine under testing.
%These techniques demand different effort from developers. 
Cross-engine differential testing is semi-automated as
developers need to decide if alarms are manifestations of real
bugs. Test transplantation is fully automated, but it can only reveal
bugs that the original tests could reveal. This study measures the
ability of these techniques in finding bugs and the human cost
associated with each technique.
